Vitis amurensis LM

### 2018-12-11 V_acerifolia_LM.Rmd
Vitis comparison

We tested leaf number and total teeth.
```{r}
skim(acerifolia, total.teeth)
ac_tt_plot <- ggplot(acerifolia, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_tt_plot <- ac_tt_plot +labs(x = "Leaf number",
                               y = "Total teeth")
ac_tt_plot

@@

We wanted to test leaf number and feret diameter ratio.
```{r}
ac_fdr_plot <- ggplot(acerifolia, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_fdr_plot <- ac_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
ac_fdr_plot
```

@@

We tested leaf number and tooth area:perimeter.
```{r}
skim(acerifolia, tooth.area.perimeter)
ac_tap_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_tap_plot <- ac_tap_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
ac_tap_plot
```

@@

We tested leaf number and tooth area:internal perimeter.
```{r}
skim(acerifolia, tooth.area.int.perimeter)
ac_taip_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_taip_plot <- ac_taip_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
ac_taip_plot
```

@@

We tested leaf number and average tooth area.
```{r}
skim(acerifolia, average.tooth.area)
ac_ta_plot <- ggplot(acerifolia, aes(x = leaf, y = average.tooth.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_ta_plot <- ac_ta_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
ac_ta_plot

>>>>

We tested leaf number and total teeth.
```{r}
skim(acerifolia, total.teeth)
ac_tt_plot <- ggplot(acerifolia, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + ylim(25, 100) + 
  scale_x_continuous(breaks = seq(0, 12, 1))
ac_tt_plot <- ac_tt_plot +labs(x = "Leaf number",
                               y = "Total teeth")
ac_tt_plot
ggsave("ac_tt.png")
```

@@

We wanted to test leaf number and feret diameter ratio.
```{r}
ac_fdr_plot <- ggplot(acerifolia, aes(x = leaf, y = feret.diameter.ratio)) + 
  geom_smooth() + theme_classic() + ylim(0.65, 0.9) + scale_x_continuous(breaks = seq(0, 12, 1))
ac_fdr_plot <- ac_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
ac_fdr_plot
ggsave("ac_fdr.png")
```

@@

We tested leaf number and tooth area:perimeter.
```{r}
skim(acerifolia, tooth.area.perimeter)
ac_tap_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.1) + scale_x_continuous(breaks = seq(0, 12, 1))
ac_tap_plot <- ac_tap_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
ac_tap_plot
ggsave("ac_tap.png")
```

@@

We tested leaf number and tooth area:internal perimeter.
```{r}
skim(acerifolia, tooth.area.int.perimeter)
ac_taip_plot <- ggplot(acerifolia, aes(x = leaf, y = tooth.area.int.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0.02, 0.16) + scale_x_continuous(breaks = seq(0, 12, 1))
ac_taip_plot <- ac_taip_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
ac_taip_plot
ggsave("ac_taip.png")
```

@@

We tested leaf number and average tooth area.
```{r}
skim(acerifolia, average.tooth.area)
ac_ta_plot <- ggplot(acerifolia, aes(x = leaf, y = average.tooth.area)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.25) + scale_x_continuous(breaks = seq(0, 12, 1))
ac_ta_plot <- ac_ta_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
ac_ta_plot
ggsave("ac_ata.png")
```

### 2018-12-11 V_aestivalis_LM.Rmd
Vitis comparison

We wanted to test leaf number and feret diameter ratio.
```{r}
av_fdr_plot <- ggplot(aestivalis, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
av_fdr_plot <- av_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
av_fdr_plot
```

@@

We tested leaf number and tooth area:perimeter.
```{r}
av_tap_plot <- ggplot(aestivalis, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
av_tap_plot <- av_tap_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
av_tap_plot
```

@@

We tested leaf number and tooth area:internal perimeter.
```{r}
av_taip_plot <- ggplot(aestivalis, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
av_taip_plot <- av_taip_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
av_taip_plot
```

@@

We tested leaf number and average tooth area.
```{r}
av_ta_plot <- ggplot(aestivalis, aes(x = leaf, y = average.tooth.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
av_ta_plot <- av_ta_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
av_ta_plot

@@

We tested leaf number and tooth teeth for 2013.
```{r}
av_tt13_plot <- ggplot(av_13, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
av_tt13_plot <- av_tt13_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
av_tt13_plot

@@

We tested leaf number and total teeth for 2015.
```{r}
av_tt15_plot <- ggplot(av_15, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
av_tt15_plot <- av_tt15_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
av_tt15_plot

>>>>

We wanted to test leaf number and feret diameter ratio.
```{r}
av_fdr_plot <- ggplot(aestivalis, aes(x = leaf, y = feret.diameter.ratio)) + 
  geom_smooth() + theme_classic() + ylim(0.65, 0.9) + scale_x_continuous(breaks = seq(0, 12, 1))
av_fdr_plot <- av_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
av_fdr_plot
ggsave("av_fdr.png")
```

@@

We tested leaf number and tooth area:perimeter.
```{r}
av_tap_plot <- ggplot(aestivalis, aes(x = leaf, y = tooth.area.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.1) + scale_x_continuous(breaks = seq(0, 12, 1))
av_tap_plot <- av_tap_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
av_tap_plot
ggsave("av_tap.png")
```

@@

We tested leaf number and tooth area:internal perimeter.
```{r}
av_taip_plot <- ggplot(aestivalis, aes(x = leaf, y = tooth.area.int.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0.02, 0.16) + scale_x_continuous(breaks = seq(0, 12, 1))
av_taip_plot <- av_taip_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
av_taip_plot
ggsave("av_taip.png")
```

@@

We tested leaf number and average tooth area.
```{r}
av_ta_plot <- ggplot(aestivalis, aes(x = leaf, y = average.tooth.area)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.25) + scale_x_continuous(breaks = seq(0, 12, 1))
av_ta_plot <- av_ta_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
av_ta_plot
ggsave("av_ata.png")
```

@@

We tested leaf number and tooth teeth for 2013.
```{r}
av_tt13_plot <- ggplot(av_13, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + ylim(25, 100) + scale_x_continuous(breaks = seq(0, 12, 1), limits = c(1, 12))
av_tt13_plot <- av_tt13_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
av_tt13_plot
ggsave("av_tt13.png")
```

@@

We tested leaf number and total teeth for 2015.
```{r}
av_tt15_plot <- ggplot(av_15, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + ylim(25, 100) + scale_x_continuous(breaks = seq(0, 12, 1), limits = c(1, 12))
av_tt15_plot <- av_tt15_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
av_tt15_plot
ggsave("av_tt15.png")
```

### 2018-12-11 V_amurensis_LM.Rmd
Vitis comparison

We tested leaf number and feret diameter ratio.
```{r}
am_fdr_plot <- ggplot(amurensis, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_fdr_plot <- am_fdr_plot +labs(x = "Leaf number",
                               y = "FDR")
am_fdr_plot

```

@@

We tested leaf number and total teeth for 2013.
```{r}
am_tt13_plot <- ggplot(am_13, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_tt13_plot <- am_tt13_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt13_plot
```

@@

We tested leaf number and total teeth for 2015.
```{r}
am_tt15_plot <- ggplot(am_15, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_tt15_plot <- am_tt15_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt15_plot
```

@@

We tested leaf number and tooth area:perimeter for 2013.
```{r}
am_tap13_plot <- ggplot(am_13, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_tap13_plot <- am_tap13_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
am_tap13_plot
```

@@

We tested leaf number and tooth area:perimeter for 2015.
```{r}
am_tap15_plot <- ggplot(am_15, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_tap15_plot <- am_tap15_plot +labs(x = "Leaf number",
                               y = "Tooth area:perimeter")
am_tap15_plot
```

@@

We tested leaf number and tooth area:internal perimeter for 2013.
```{r}
am_taip13_plot <- ggplot(am_13, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_taip13_plot <- am_taip13_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
am_taip13_plot
```

@@

We tested leaf number and tooth area:internal perimeter for 2015.
```{r}
am_taip15_plot <- ggplot(am_15, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_taip15_plot <- am_taip15_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
am_taip15_plot
```

@@

We tested leaf number and average tooth area for 2013.
```{r}
am_ata13_plot <- ggplot(am_13, aes(x = leaf, y = average.tooth.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_ata13_plot <- am_ata13_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata13_plot
```

@@

We tested leaf number and average tooth area for 2015.
```{r}
am_ata15_plot <- ggplot(am_15, aes(x = leaf, y = average.tooth.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_ata15_plot <- am_ata15_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata15_plot
```

>>>>

We tested leaf number and feret diameter ratio.
```{r}
am_fdr_plot <- ggplot(amurensis, aes(x = leaf, y = feret.diameter.ratio)) + 
  geom_smooth() + theme_classic() + ylim(0.65, 0.9) + scale_x_continuous(breaks = seq(0, 13, 1))
am_fdr_plot <- am_fdr_plot +labs(x = "Leaf number",
                               y = "FDR")
am_fdr_plot
ggsave("am_fdr.png")
```

@@

We tested leaf number and total teeth for 2013.
```{r}
am_tt13_plot <- ggplot(am_13, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + ylim(25, 100) + scale_x_continuous(breaks = seq(0, 12, 1))
am_tt13_plot <- am_tt13_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt13_plot
ggsave("am_tt13.png")
```

@@

We tested leaf number and total teeth for 2015.
```{r}
am_tt15_plot <- ggplot(am_15, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + ylim(25, 100) + scale_x_continuous(breaks = seq(0, 12, 1))
am_tt15_plot <- am_tt15_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt15_plot
ggsave("am_tt15.png")
```

@@

We tested leaf number and tooth area:perimeter for 2013.
```{r}
am_tap13_plot <- ggplot(am_13, aes(x = leaf, y = tooth.area.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.1) + scale_x_continuous(breaks = seq(0, 13, 1))
am_tap13_plot <- am_tap13_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
am_tap13_plot
ggsave("am_tap13.png")
```

@@

We tested leaf number and tooth area:perimeter for 2015.
```{r}
am_tap15_plot <- ggplot(am_15, aes(x = leaf, y = tooth.area.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.1) + scale_x_continuous(breaks = seq(0, 12, 1))
am_tap15_plot <- am_tap15_plot +labs(x = "Leaf number",
                               y = "Tooth area:perimeter")
am_tap15_plot
ggsave("am_tap15.png")
```

@@

We tested leaf number and tooth area:internal perimeter for 2013.
```{r}
am_taip13_plot <- ggplot(am_13, aes(x = leaf, y = tooth.area.int.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0.02, 0.16) + scale_x_continuous(breaks = seq(0, 13, 1))
am_taip13_plot <- am_taip13_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
am_taip13_plot
ggsave("am_taip13.png")
```

@@

We tested leaf number and tooth area:internal perimeter for 2015.
```{r}
am_taip15_plot <- ggplot(am_15, aes(x = leaf, y = tooth.area.int.perimeter)) + 
  geom_smooth() + theme_classic() + ylim(0.02, 0.16) + scale_x_continuous(breaks = seq(0, 13, 1))
am_taip15_plot <- am_taip15_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
am_taip15_plot
ggsave("am_taip15.png")
```

@@

We tested leaf number and average tooth area for 2013.
```{r}
am_ata13_plot <- ggplot(am_13, aes(x = leaf, y = average.tooth.area)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.25) + scale_x_continuous(breaks = seq(0, 13, 1))
am_ata13_plot <- am_ata13_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata13_plot
ggsave("am_ata13.png")
```

@@

We tested leaf number and average tooth area for 2015.
```{r}
am_ata15_plot <- ggplot(am_15, aes(x = leaf, y = average.tooth.area)) + 
  geom_smooth() + theme_classic() + ylim(0, 0.25) + scale_x_continuous(breaks = seq(0, 13, 1))
am_ata15_plot <- am_ata15_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata15_plot
ggsave("am_ata15.png")
```
